---
title: "framingham"
author: "jy"
date: "July 27, 2016"
output: html_document
---
### Subject
Logistical regression using the Farmingham heart disease data set. Data is available in **'datasets'** folder.

### Data
Check out the data structure and get a sample of data:
```{r, echo=FALSE, warning=FALSE}
framingham <- read.csv("datasets/framingham.csv")
str(framingham)
head(framingham)
```
Note that **TenYearCHD** is the **dependent** variable, indicating whether or not the subject had Coronary Heart Disease within 10 years of the data being collected.

### Process data for analysis
Split the data between training and test sets (65\% in training set)
```{r, warning=FALSE}
library(caTools)
set.seed(1000)
split <- sample.split(framingham$TenYearCHD, SplitRatio=0.65)
train <- subset(framingham, split==TRUE)
test <- subset(framingham, split==FALSE)
```

### Logistic Regression Model
Use all independent variables against the dependent variable. (For logistic regression family=binomial)
```{r, warning=FALSE, message=FALSE}
framinghamLog <- glm(TenYearCHD ~ ., data=train, family=binomial)
```
#### Summary of the model:
```{r, echo=FALSE, warning=FALSE, message=FALSE}
summary(framinghamLog)
```
### Results
* male, age, prevalentStroke, total cholesterol, systolic blood pressure, glucose are all significant in the model
* cigarettes per day and prevalent hypertension are somewhat significant
* coefficients are positive for all these variables, meaning that they contribute to a higher probability of ten year coronary heart disease

### Prediction
Use the model to make predictions on the test set.(type=response for probabilities)
```{r, warning=FALSE, message=FALSE}
predictTest <- predict(framinghamLog, type="response", newdata=test)
```
Set a treshold value at 0.5 to create a confusion matrix
```{r, warning=FALSE, message=FALSE}
table(test$TenYearCHD, predictTest >0.5)
```
* with this threshold, the model predicts an outcome of 1 (TenYearCHD) rarely, indicating that it doesn't find many cases where 10 yr CHD risk is above 50\%

#### Check the Accuracy of the model
```{r}
(1069+11)/(1069+6+187+11)
```
Accuracy is high because of the high score with true negatives. True positives not that great.

For comparison, if the model just predicted everybody as negative (not getting 10 yr CHD), accuracy would be:
```{r}
(1069+6)/(1069+6+187+11)
```
Basically the same as the model! But the model may still be valuable by varying the threshold.

#### Check the Value of the model
Computer out-of-sample AUC (area under curve)
```{r, warning=FALSE, message=FALSE}
library(ROCR)
ROCRpred <- prediction(predictTest, test$TenYearCHD)
as.numeric(performance(ROCRpred, "auc")@y.values)
```
An AUC of about 74% indicates the model can differentiate between low risk and high risk patients pretty well. 

#### Conclusion
* the model does not do well at predicting 10-year risk of CHD above 50\% (predicting only 11 of 198 cases)
* the model does pretty well at differentiating between high risk and low risk patients, with an out-of-sample AUC of 0.74 (not totally sure what this means)
* also, some of the variables identified as significant suggest possible interventions to reduce risk of CHD

END OF LESSON MODULE

#### Questions
Does the model do better with lower threshold?
Set a treshold value at 0.25 to create a confusion matrix
```{r, warning=FALSE, message=FALSE}
table(test$TenYearCHD, predictTest >0.25)
```
Accuracy:
```{r}
(940+74)/(940+135+124+74)
```
Lower threshold leads to less accuracy.
```{r, echo=FALSE}
fp1 <- 6/(1069+6)
fn1 <- 187/(187+11)
fp2 <- (135)/(135+940)
fn2 <- 124/(124+74)
p1 <- 11/(11+6)
p2 <- 74/(135+74)
```
* False positive is now: `r fp2` compared to `r fp1`
* False negative is now: `r fn2` compared to `r fn1`

So the lower threshold is better if you want to err on the side of catching high risk patients, even though you will be wrong in your prediction more than you will be right.

Also, precision is not great:  
* 25\% threshold: `r p2`  
* 50\% threshold: `r p1`