---
title: "framingham"
author: "jy"
date: "July 27, 2016"
output: html_document
---
### Subject
Logistical regression using the Farmingham heart disease data set. Data is available in 'datasets' folder.

### Data
Check out the data structure:
```{r, echo=FALSE, warning=FALSE}
framingham <- read.csv("datasets/framingham.csv")
str(framingham)
```
Note that TenYearCHD is the dependent variable, indicating whether or not the subject had Coronary Heart Disease within 10 years of the data being collected.

### Process data for analysis
Split the data between training and test sets (65\% in training set)
```{r, warning=FALSE}
library(caTools)
set.seed(1000)
split <- sample.split(framingham$TenYearCHD, SplitRatio=0.65)
train <- subset(framingham, split==TRUE)
test <- subset(framingham, split==FALSE)
```
### Logistic Regression Model
Use all independent variables against the dependent variable. (For logistic regression family=binomial)
```{r, warning=FALSE, message=FALSE}
framinghamLog <- glm(TenYearCHD ~ ., data=train, family=binomial)
```
#### Summary of the model:
```{r, echo=FALSE, warning=FALSE, message=FALSE}
summary(framinghamLog)
```
### Results
* male, age, prevalentStroke, total cholesterol, systolic blood pressure, glucose are all significant in the model
* cigarettes per day and prevalent hypertension are somewhat significant
* coefficients are positive for all these variables, meaning that they contribute to a higher probability of ten year coronary heart disease

### Prediction
Use the model to make predictions on the test set.(type=response for probabilities)
```{r, warning=FALSE, message=FALSE}
predictTest <- predict(framinghamLog, type="response", newdata=test)
```
Set a treshold value at 0.5 to create a confusion matrix
```{r, warning=FALSE, message=FALSE}
table(test$TenYearCHD, predictTest >0.5)
```
* with this threshold, the model predicts an outcome of 1 (TenYearCHD) rarely, indicating that it doesn't find many cases where 10 yr CHD risk is above 50\%

#### Check the accuracy of the model
```{r}
(1069+11)/(1069+6+187+11)
```

