---
title: "wk4-trees-1-supreme-court"
author: "jy"
date: "August 4, 2016"
output: html_document
---

### Get the data, set factors
```{r, echo=FALSE, results='hide'}
stevens <- read.csv("datasets/stevens.csv",stringsAsFactors = FALSE)
str(stevens)
stevens$Circuit <- as.factor(stevens$Circuit)
stevens$Issue <- as.factor(stevens$Issue)
stevens$Petitioner <- as.factor(stevens$Petitioner)
stevens$Respondent <- as.factor(stevens$Respondent)
stevens$LowerCourt <- as.factor(stevens$LowerCourt)
#str(stevens)
```

```{r, echo=FALSE}
str(stevens)
```
includes 9 variables, including:
* 8 independent variables
* 1 dependent variable: Reverse (indicating if the Judge reversed lower court)

### Set up training  and test set - 70% of data in training
```{r, warning=FALSE}
library(caTools)
set.seed(3000)
split <- sample.split(stevens$Reverse, SplitRatio=0.7)
Train <- subset(stevens, split==TRUE)
Test <- subset(stevens, split==FALSE)
```

### Create CART model (Classification and Regression Tree)
```{r, warning=FALSE}
library(rpart)
StevensTree <- rpart(Reverse~Circuit+Issue+Petitioner+Respondent+LowerCourt+Unconst, data=Train, method="class", control=rpart.control(minbucket=25))
```
(minbucket=25 to ensure sufficient cases are in each bucket)

### Check out the Decision Tree on the Training Data
```{r, echo=FALSE, warning=FALSE}
library(rpart.plot)
prp(StevensTree)
```
  
Follow the tree branches to determine whether Justice Stevens is likely to have upheld (0) or reversed (1) the lower court decisions in the training data set.
